Carrier phase and amplitude estimation for phase shift keying using pilots and data

### 2014-06-19 response2.tex
minr?

\item \textbf{Comment:} ``we assume that the time-offset has been previously handled'' $\to$ perhaps some motivation for this assumption and the consequences with respect to the system model would be in place \\
\textbf{Response:}  The assumption of an accurate time offset estimator is common in this literature~\cite{ViterbiViterbi_phase_est_1983,Cowley_ref_sym_carr_1998,Wilson1989,Makrakis1990,Liu1991,Mackenthun1994,Sweldens2001,McKilliamLinearTimeBlockPSK2009,Divsalar1990} and is unlikely to come as a surprise to the intended audience.  There exist numerous estimators for the time offset in the literature.  We have added the sentence

>>>>

\item \textbf{Comment:} ``we assume that the time-offset has been previously handled'' $\to$ perhaps some motivation for this assumption and the consequences with respect to the system model would be in place \\
\textbf{Response:}  %The assumption of an accurate time offset estimator is common in this literature~\cite{ViterbiViterbi_phase_est_1983,Cowley_ref_sym_carr_1998,Wilson1989,Makrakis1990,Liu1991,Mackenthun1994,Sweldens2001,McKilliamLinearTimeBlockPSK2009,Divsalar1990} and is unlikely to come as a surprise to the intended audience.  
There exist numerous estimators for the time offset in the literature.  We have added the sentence
